%% ------------------------------ Abstract ---------------------------------- %%
\begin{abstract}

Microblogs are a popular way to keep abreast with important information about different topics. Half a billion people across the world use Twitter, and and 175 million tweets are posted each day. With so much available data, summarization is critical. This thesis examines the problem of summarizing tweets from a single Twitter user over the the course of a few weeks to a month, between 35 and 60 tweets. The summarization takes the form of a subset of those tweets. We have developed and compared algorithms that can be used to summarize tweets in this way. We describe an unsupervised algorithm that clusters tweets by topic, using information retrieval techniques, and then selects a specific tweet from each cluster, relying on sentiment. An experimental evaluation shows that this approach produces results that are not as good as those of human summarizers, but are better than an existing baseline for such summaries.

\end{abstract}


%% ---------------------------- Copyright page ------------------------------ %%
%% Comment the next line if you don't want the copyright page included.
\makecopyrightpage

%% -------------------------------- Title page ------------------------------ %%
\maketitlepage

%% -------------------------------- Dedication ------------------------------ %%
\begin{dedication}
\centering To my family, for their support, love  and encouragement\\
\centering To my advisor, Dr Robert St. Amant, for his guidance in research\\
\centering To all of my friends, for their help and motivation
\end{dedication}

%% -------------------------------- Biography ------------------------------- %%
\begin{biography}

Shishir Mahesh Kakaraddi was born on 21st July, 1987 in Belgaum, Karnataka, India. He received a Bachelor of Engineering degree in Information Science from M S Ramaiah Institute of Technology, Bangalore, India. He worked at IBM India Pvt Ltd as Software Developer for 11 months and then he joined North Carolina State University to pursue his Masters degree in the Department of Computer Science. After completion of his Masters degree he will be joining VMware in Palo Alto, California as a Member of Technical Staff.

\end{biography}

%% ----------------------------- Acknowledgements --------------------------- %%
\begin{acknowledgements}

I would like to thank my advisor Dr. Robert St. Amant who provided his professional advice on research ideas and dissertation writing. I also want to thank other committee members, Dr.Edward Gehringer and Dr. Christopher Healey,  for spending their time reading my  and contributing valuable comments and suggestions.Thanks to Dr. Tessa Lau, Research Staff Member, IBM Research for motivating me to do research and for introducing me to my advisor. I want to thank my friends Sridevi Venugopal and Thothathri Srinivasan for providing their opinions on several intermediate results. I would like to thank Arpan Chakraborty, Sina Bahram, Srinath Ravindran and others in the Knowledge Discovery Lab for their suggestions. I would also like to thank everybody who helped me with the evaluation of my research.

\end{acknowledgements}


\thesistableofcontents

\thesislistoftables

\thesislistoffigures
